|

### 2022-12-12 r-report/Paper.tex

The question arises, how China plans to curb its emissions. At the
United Nations General Assembly in 2020, Chinese President Xi Jinping
announced the goal of Chinese carbon neutrality before 2060
\citep{Jinping2020}. This was the first time China officially committed
to a long-term emissions reductions goal \citep{CAT2022}. One year
later, in November 2021, ahead of COP26, China submitted its updated NDC
to the UNFCCC. Accordingly, the country plans to peak its carbon
emissions before 2030, decrease the carbon intensity of GDP by over 65\%
(relative to 2005), have around 25\% of non-fossil fuels in primary
energy consumption by 2030, increase the forest stock volume by six
billion cubic meters until 2030 and have 1,200 GW of wind and solar
power capacity installed by the same year \citep{China2022}. Although
some of these objectives are vague to some degree, and the emissions
reduction target is only a relative goal, the ambitions China has set
for itself are a marked improvement over the targets set out in the
previous 2016 NDC. Additionally, it is important to note that these
goals are unconditional and hence not relying on external climate
finance. China has adopted numerous policies to support its
international targets, such as the ``Working Guidance for Carbon Dioxide
Peaking and Carbon Neutrality'' and the ``Action Plan for Carbon Dioxide
Peaking Before 2030''. The former spells out a set of principles and
sectoral goals to achieve carbon dioxide peaking and carbon neutrality,
among them the need to exercise nationwide planning and the
prioritization of conversing energy (Department of Resource Conservation
and Environmental Protection, 2021a). The latter defines key tasks for
driving the low-carbon energy transition or saving energy, carbon
emission mitigation and efficiency improvement \citep{DRCEP2021b}. With
its ``14th Five-Year Plan on Renewable Energy'', the country aims to
further accelerate its renewable energy expansion. By 2025, 33\% of
electricity ought to be supplied by renewable sources (18\% non-hydro),
which could decrease annual carbon emissions by 2.6 gigatons
\citep{Zhou2022}.

@@

China itself assesses its responsibility for climate change mitigation
measures very differently though. In its 2021 NDC update, China assigns
responsibility for global warming to developed countries. It were their
emissions that had caused the dramatic increase of GHGs in the
atmosphere. China, on the other hand, was a developing country, thereby
having the right to develop \citep{China2022}.

@@

Nevertheless, one needs to consider that development is not equally
distributed in China. The rural population has benefited significantly
less from the economic development than the urban population (East-West
divide) \citep{Knight2004}. However, the argument that one still has the
right to predominantly emissions-based development (as in 1992) is no
longer in line with China's current status as the world's biggest
emitter. Hence, China's NDC's storyline, which seeks the main
responsibility for climate change in developed nations, is too
undercomplex and does not do justice to the evolved realities.

@@

  \bibliography{packages.bib}

>>>>

The question arises, how China plans to curb its emissions. At the
United Nations General Assembly in 2020, Chinese President Xi Jinping
announced the goal of Chinese carbon neutrality before 2060
\citep{Jinping2020}. This was the first time China officially committed
to a long-term emissions reductions goal \citep{CAT2022}. One year
later, in November 2021, ahead of COP26, China submitted its updated NDC
to the UNFCCC. Accordingly, the country plans to peak its carbon
emissions before 2030, decrease the carbon intensity of GDP by over 65\%
(relative to 2005), have around 25\% of non-fossil fuels in primary
energy consumption by 2030, increase the forest stock volume by six
billion cubic meters until 2030 and have 1,200 GW of wind and solar
power capacity installed by the same year \citep{China2022}. Although
some of these objectives are vague to some degree, and the emissions
reduction target is only a relative goal, the ambitions China has set
for itself are a marked improvement over the targets set out in the
previous 2016 NDC. Additionally, it is important to note that these
goals are unconditional and hence not relying on external climate
finance. China has adopted numerous policies to support its
international targets, such as the ``Working Guidance for Carbon Dioxide
Peaking and Carbon Neutrality'' and the ``Action Plan for Carbon Dioxide
Peaking Before 2030''. The former spells out a set of principles and
sectoral goals to achieve carbon dioxide peaking and carbon neutrality,
among them the need to exercise nationwide planning and the
prioritization of conversing energy \citep{DRCEP2021a}. The latter
defines key tasks for driving the low-carbon energy transition or saving
energy, carbon emission mitigation and efficiency improvement
\citep{DRCEP2021b}. With its ``14th Five-Year Plan on Renewable
Energy'', the country aims to further accelerate its renewable energy
expansion. By 2025, 33\% of electricity ought to be supplied by
renewable sources (18\% non-hydro), which could decrease annual carbon
emissions by 2.6 gigatons \citep{Zhou2022}.

@@

China itself assesses its responsibility for climate change mitigation
measures very differently though. In its 2021 NDC update, China assigns
responsibility for global warming to developed countries. It were their
emissions that had caused the dramatic increase of GHGs in the
atmosphere. China, on the other hand, was a developing country, thereby
having the right to develop \citep{China2021}.

@@

Nevertheless, one needs to consider that development is not equally
distributed in China. The rural population has benefited significantly
less from the economic development than the urban population
\citep[East-West divide,][]{Knight2004}. However, the argument that one
still has the right to predominantly emissions-based development (as in
1992) is no longer in line with China's current status as the world's
biggest emitter. Hence, China's NDC's storyline, which seeks the main
responsibility for climate change in developed nations, is too
undercomplex and does not do justice to the evolved realities.

@@

  \bibliography{anna.bib,fabian.bib,packages.bib}
